Experimental Analysis of a Spatialised Audio Interface for People with Visual Impairments

### 2019-11-07 paper.tex
revised abstract and conclusions

\title{NEW TITLE}

@@

\begin{abstract}
  The ActiVis project's aim is to build a mobile guidance aid to help people with limited vision find objects in an unknown environment.
  This system uses bone-conduction headphones to transmit audio signals to the user and requires an effective non-visual interface.
  In prior work, we implemented and tested a audio-based interface that uses a spatialised signal to convey a target's position on the horizontal plane. 
  This approach was shown to work well and in this work we expand the number of tests and metrics to provide a more more in-depth evaluation of the proposed audio interface.
  Specifically, we used a larger number of participants and found design limitations and a Fitts's Law-compliant trend that we can use to improve and refine the audio signals. 
\end{abstract}

@@

The ActiVis\footnote{https://lcas.github.io/ActiVis/} project is working towards building an indoor mobile navigation aid for people with vision impairments that can guide them to their destination in the last leg of their journey (the so-called `last 10-yard problem').
Improvements to computer vision and machine learning techniques, as well as mobile commuting hardware improvements are exploited to make this system possible.
In particular, techniques from the active vision field are being used to enable a mobile device to gather information on the surrounding environment and use it to generate guidance instructions for a user with limited or no vision.
However, in literature, these techniques are typically limited to electro-mechanical servos~\citep{bajcsy2018revisiting} and in this project, we attempt to find out if the same techniques can also be used to direct a user's attention to a certain point. 
In previous work we implemented a prototype system that uses active vision and machine learning models to gather information and help a person find objects in an unknown environment, showing that these techniques can indeed successfully be applied to humans as well~\citep{lock2019active}.

@@

\begin{figure}[t]
  \centering
  \subfloat[]{\label{fig:tango}\includegraphics[width=0.4\columnwidth]{figures/tango_asus.jpeg}}
~
  \subfloat[]{\label{fig:tango-headphone}\includegraphics[width=0.3\columnwidth]{figures/tango_headphone.png}}
~
  \subfloat[]{\label{fig:participant}\includegraphics[width=0.2\columnwidth]{figures/vi_participant.pdf}}
  \caption{Pictures of the latest Tango mobile phone (left), the former Tango tablet and the bone-conduction headphones used in this work (centre), and a participant with visual impairments during an experiment (right).}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \subfloat[]{\label{fig:cam-coords}\includegraphics[width=0.3\columnwidth]{figures/camera_coordinate.pdf}}
\hfil
  \subfloat[]{\label{fig:pitch-gain}\includegraphics[clip, trim=0 0 0 40, width=0.7\columnwidth]{figures/pitch_gain_function.png}}
  \caption{The reference system used by the guidance interface showing the camera vector and pan and elevation angles (left) and the pitch gain function used to convey the target's elevation angle (right). Note the logarithmic scale of the frequency axis.}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[clip=true, trim=0 120 80 50, width=\columnwidth]{figures/pipeline.pdf}
  \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal.}\label{fig:pipeline}
\end{figure}

@@

In this work, we expanded upon the initial investigation from~\citep{lock2019bone} and performed a wider number of tests with more participants where we investigated using spatialised sound with a varying tone to direct a user's gaze in more detail.
We found that the blindfolded participants and participants with severe sight impairments had similar levels of performance in localising sound and differentiating between tones. 
We also found that both groups managed to find a set of targets with similar levels of accuracy.
However, the blindfolded group managed to outperform the group with severe sight impairments in terms of time to find the target. 
We also tested different pitch gain gradient settings for the pitch and found that the performance in the pan dimension that uses spatialised signals, is independent of the pitch gradient setting.
Furthermore, we found a speed-accuracy trade off between the settings, where a steeper pitch gain gradient produces a smaller angular error at the cost of decreased time performance. 
This, along with the Fitts-like relationship that was found, can be used to improve and refine the interface in order to prioritise speed or accuracy and produce the desired output.

The next steps for the project is to implement this interface into a guidance system and test the complete system's performance. 
Implementing an auto-adaptive interface scheme can also now be considered.

>>>>

\title{Experimental Analysis of a Spatialised Audio Interface for People with Visual Impairments}

@@

\begin{abstract}
  Sound perception is a fundamentally important skill for many people with severe sight impairments. The research presented in this paper is part of the ActiVis project, the aim of which is to build a mobile guidance aid to help people with limited vision find objects in an unknown environment.
  This system requires an effective non-visual interface and therefore uses bone-conduction headphones to transmit audio instructions to the user.
  It has been implemented and tested with spatialised audio cues, which convey the direction of a predefined target in 3D space.
  We present an in-depth evaluation of the audio interface with several experiments that involve a large number of participants, both blindfolded and with actual visual impairments. We analyse pros and cons of our design choices, and found that a Fitts's Law metric can be used to improve and refine the quality of the audio interface in future mobile navigation aids. \tofix{Reworded, check if OK}
\end{abstract}

@@

The ActiVis\footnote{https://lcas.github.io/ActiVis/} project aims to build an indoor mobile navigation aid for people with vision impairments that can guide them to their destination in the last leg of their journey (the so-called `last 10-yard problem').
Improvements to computer vision and machine learning techniques, as well as mobile commuting hardware improvements are exploited to make this system possible.
In particular, techniques from the active vision field are being used to enable a mobile device to gather information on the surrounding environment and use it to generate guidance instructions for a user with limited or no vision.
However, in literature, these techniques are typically limited to electro-mechanical servos~\citep{bajcsy2018revisiting} and in this project, we attempt to find out if the same techniques can also be used to direct a user's attention to a certain point. 
In previous work we implemented a prototype system that uses active vision and machine learning models to gather information and help a person find objects in an unknown environment, showing that these techniques can indeed successfully be applied to humans as well~\citep{lock2019active}.

@@

\begin{figure}[t]
  \centering
  \subfloat[]{\label{fig:tango}\includegraphics[width=0.4\columnwidth]{figures/tango_asus.jpeg}}
~
  \subfloat[]{\label{fig:tango-headphone}\includegraphics[width=0.3\columnwidth]{figures/tango_headphone.png}}
~
  \subfloat[]{\label{fig:participant}\includegraphics[width=0.2\columnwidth]{figures/vi_participant.pdf}}
  \caption{Pictures of the latest Tango mobile phone (left), the former Tango tablet and the bone-conduction headphones used in this work (centre), and a participant with visual impairments during an experiment (right). \tofix{Update this figures to differ from AEIT)}}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \subfloat[]{\label{fig:cam-coords}\includegraphics[width=0.3\columnwidth]{figures/camera_coordinate.pdf}}
\hfil
  \subfloat[]{\label{fig:pitch-gain}\includegraphics[clip, trim=0 0 0 40, width=0.7\columnwidth]{figures/pitch_gain_function.png}}
  \caption{The reference system used by the guidance interface showing the camera vector and pan and elevation angles (left) and the pitch gain function used to convey the target's elevation angle (right). Note the logarithmic scale of the frequency axis. \tofix{Update this figure (e.g. use colors) to differ from AEIT)}}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[clip=true, trim=0 120 80 50, width=\columnwidth]{figures/pipeline.pdf}
  \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal. \tofix{Update this figure (e.g. use colors) to differ from AEIT)}}\label{fig:pipeline}
\end{figure}

@@

In this paper we investigated the use of spatialised audio interface with varying pitch to guide a visually impaired user in a target pointing task.
We found that the blindfolded participants and those with severe sight impairments performed similarly in localising sound sources and differentiating between tones. 
We also found that both groups were able to find a set of randomly distribute set of direction targets with similar levels of accuracy.
However, the blindfolded group outperformed the one with severe sight impairments in terms of time-to-target. 
We further tested different pitch settings and found that the user performance in the pan dimension, based on spatialised cues, is independent of such settings.
Moreover, we noticed a speed/accuracy trade-off between the settings, where a higher pitch setting produces a smaller angular error, but at the cost of reducing the time performance (i.e. higher time-to-target). 
These results, together with a a Fitts's Law analysis that confirms its applicability to this type of audio interface, provide a useful baseline to improve and refine the latter in future applications, prioritising speed or accuracy to produce the desired output.
\tofix{I reworded a few bits, check if still correct}

% The next steps for the project is to implement this interface into a guidance system and test the complete system's performance. 
% Implementing an auto-adaptive interface scheme can also now be considered.
\tofix{A little more effort in your (hypothetical) plans for future work. You could expand more the user-adaptation concept -- e.g. adapt to different users, or to the performance variations of the same user over time (like the ``progressive co-adaptation'' of~\cite{gallina2015progressive}). Also, what about adding extra modalities, like voice instructions or device vibrations?}
